\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

  \resumeSubheading
        {Data Science Wizards (DSW)}
        {Open Source Engineer Intern}
        {Thane, Maharashtra}
        {March 2024 -- Current}
        \resumeItemListStart
          \resumeItem{
            Provided support to clients on various open-source tools and software, including \textbf{Docker, Redis, and Kafka}.
          }
          \resumeItem{
            Gained extensive hands-on experience with \textbf{Kubernetes (K8s)}, diving deep into its core concepts and practical applications.
          }
          \resumeItem{
            Created and managed K8s clusters of varying complexities:
            \begin{itemize}
              \item Single-node clusters using \textbf{Minikube}
              \item Multi-node clusters (\textbf{1 master, 2 worker nodes})
              \item \textbf{High-availability clusters} (3 masters, 3 worker nodes)
              \item \textbf{Bare-metal clusters for OpenShift}
            \end{itemize}
          }
          \resumeItem{
            \textbf{Deployed open-source projects (EFK stack)} on client's \textbf{Tanzu Kubernetes} environments across \textbf{pre-prod, prod, and DR} setups.
          }
          \resumeItem{
            Consulted on and resolved multiple issues in pre-prod and UAT environments, including \textbf{fixing connectivity problems between external services and internal pods}.
          }
        \resumeItemListEnd

    \resumeSubheading
      {RedCarpetUp}
      {Rust \& Javascript WASM Development Intern}
      {Remote}
      {Nov 2023 -- April 2024}
      \resumeItemListStart
        \resumeItem{Developed features and added support for core libraries like Jsonnet in Rust, creating bindings between JavaScript and the custom Javy runtime.}       \resumeItem{Integrated the Jsonnet library into the existing codebase by building a Rust bridge to enable communication between JavaScript and C++.}
        \resumeItem{Integrated Rust and JavaScript code using WebAssembly bridges like WASI, enabling efficient communication between the languages.}
      \resumeItemListEnd

    \resumeSubheading
      { Pi R Square Digital Solutions Pvt Ltd}
      {Full Stack Developer}
      {Pune, Maharashtra (Remote)}
      {Feb 2023 -- Oct 2023}
      \resumeItemListStart
      % {As a Full Stack Developer for Pi R Square, I am responsible for the development of the company's website and web applications. In this role, I am also responsible for the maintenance of the company's IT infrastructure, ensuring that all systems are up-to-date and secure. Here are some of my achievements in this role:}

        \resumeItem{Spearheaded the migration from v1 API to v2, \textbf{enhancing system reliability and performance}}
        \resumeItem{Designed and optimized various AWS Lambda functions, one of which drastically reduced \textbf{video generation time from 11-15 seconds to a significantly lower time}. Achieved this \textbf{by optimizing FFmpeg commands and reducing video frame rate} for static images.}
        \resumeItem{Managed and improved the frontend codebase, focusing on enhancing user experience and interface.}
        \resumeItem{Implemented React lazy loading, successfully \textbf{reducing bundling time and improving the application's performance}.}
        \resumeItem{Enhanced code quality by \textbf{componentizing various parts of the website}, resulting in a more maintainable and scalable codebase.}
      \resumeItemListEnd

    \resumeSubheading
      {NixonBit}
      {Full Stack Developer}
      {Noida, Utter Pradesh (Remote)}
      {Jun 2022 \textbf{--} Dec 2022}
      \resumeItemListStart

        \resumeItem{Collaborated in the team to develop a social media platform, Bealive, \textbf{focusing on backend functionalities} such as user \textbf{authentication}, \textbf{data management}, and \textbf{API integration}.}
        \resumeItem{\textbf{Played an integral role in building an e-commerce} platform, implementing backend logic for product catalog, shopping cart, and order processing.}
        \resumeItem{\textbf{Worked with the frontend development team}, focusing on \textbf{enhancing user interfaces and user experiences} for client projects.}
        \resumeItem{Involved in the \textbf{development of an E-management software} for schools, Eclump, \textbf{working on features} related to the student \textbf{fee structure, fee history, and other administrative functionalities}.}
        \resumeItem{Made significant contributions to various projects, resulting in improved functionality and user experience.}
        \resumeItem{Demonstrated proficiency in a variety of programming languages, frameworks, and tools, showcasing versatility and adaptability.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
