
\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{VectoRapid} $|$ \emph{\href{https://github.com/QuantumMesh/VectoRapid.git}{\faExternalLink - Private }}}{}
        \resumeItemListStart
            \resumeItem{Engineering a \textbf{high-performance, scalable vector database using Rust}, tailored for computational efficiency in high-throughput tasks. Chose Rust for its strong type checking, memory safety features, and low-level control.}
            \resumeItem{\textbf{Utilized SIMD (Single Instruction, Multiple Data)} registers for \textbf{high-speed vector similarity} calculations. Employed Rust's \texttt{unsafe} blocks to tap into low-level machine operations.}
            \resumeItem{\textbf{Integrated RocksDB as the storage engine}, optimized for write-heavy workloads. Implemented hierarchical k-means clustering algorithms to accelerate query times.}
            \resumeItem{\textbf{Leveraged HNSW (Hierarchical Navigable Small World) graphs} for efficient nearest-neighbor search within identified sub-clusters.}
            \resumeItem{Designed the system to be algorithm-agnostic, offering users the flexibility to operate in a standard mode or customize the database with advanced algorithms for specialized needs.  }
        \resumeItemListEnd

        \vspace{7pt}
        \resumeProjectHeading
          {\textbf{Pose Tracking Application} $|$ \emph{\href{https://github.com/rahul007-bit/ExerciseEvaluator.git}{\faExternalLink}}}{}
            \resumeItemListStart
              \resumeItem{Developed a pose tracking application as a personal project, leveraging the MediaPipe package for pose landmark detection.}
              \resumeItem{The application allows users to track their pose and identifies the next pose for a given exercise. This is achieved by processing images or videos, identifying key body locations, and analyzing posture.}
              \resumeItem{The application provides real-time analysis of the user's posture and suggests the next pose for the exercise, improving the efficiency and effectiveness of the exercise.}
              \resumeItem{The project showcases my understanding of machine learning concepts and my ability to apply them in a practical setting.}
            \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Reimbursement} $|$ \emph{\href{https://github.com/rahul007-bit/Reimbursement.git}{\faExternalLink}}}{}
            \resumeItemListStart
            \resumeItem{Developed a reimbursement management platform as part of a college project, transforming the traditional offline reimbursement process into an efficient online system.}
            \resumeItem{The platform enables users (students and staff) to request reimbursements online, eliminating the need for physical forms and reducing processing time.}
            \resumeItem{Implemented features for report generation and graphical analysis, providing insights into reimbursement trends and improving decision-making.}
            \resumeItem{The platform streamlines the reimbursement process, making it more efficient and user-friendly.}
            \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{Storage System} $|$ \emph{\href{https://github.com/rahul007-bit/storage-system}{\faExternalLink}}}{}
            \resumeItemListStart
              \resumeItem{Developed an express.js application that enables users to create a store for uploading various types of files such as images, videos, mp3, and text.}
              \resumeItem{The main objective of the application was to merge audio and image files, convert text to audio, merge video and audio files, and merge multiple video files.}
              \resumeItem{The project showcases my understanding of file handling, merging, and processing in a server-side application, as well as my ability to use express.js for building web applications.}
            \resumeItemListEnd

    \resumeSubHeadingListEnd
