\section{Research Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Max Planck Institute for Intelligent Systems}{Stuttgart, Baden\textbf{-}Württemberg, Germany}
      {Undergraduate Researcher}{Jun 2022 \textbf{--} Aug 2022, Internship}
        \resumeItemListStart
            \resumeItem{Worked in the Robotics, Collectives and Learning subgroup at the Physical Intelligence Department with former Ph.D. students Sinan Özgün Demir and Alp Can Karacakol on a project about 3D printing and heat-assisted magnetic programming of soft machines under the supervision of Prof. Dr. Metin Sitti.}
            \resumeItem{Updated a ROS package for converting 3D motion controller events to ROS messages so that it synchronously operates at any given loop rate with C++.}
            \resumeItem{Implemented an Arduino Mega driver for controlling a fluid dispenser, a laser, thermocouples, and a coil set. Updated ROS nodes for parsing G-codes and controlling stage movement and built the ROS-Arduino communication network to simulate a 3D printing and magnetic programming process with Python.}
            \resumeItem{Designed the project's system and software architecture, algorithm flowchart, and state machine diagram. Implemented and debugged ROS nodes by validating each corresponding hardware component functions correctly.}
        \resumeItemListEnd

    % \vspace{14pt}

    \resumeSubheading
      {Nanonetworking Research Group, Boğaziçi University}{Istanbul, Turkey}
      {Undergraduate Researcher}{Oct 2021 \textbf{--} Jun 2022, Part-time}
        \resumeItemListStart
            \resumeItem{Worked on the project “Design and Implementation of Molecular Communication Systems Using Index Modulation” under the supervision of Prof. Dr. Ali Emre Pusane.}
            \resumeItem{Simulated the Brownian motion of molecules in a SISO MCvD system and predicted simulation parameters such as receiver radius, diffusion coefficient, and transmitter-receiver distance using CNNs with Keras and TensorFlow.}
            \resumeItem{Plotted the arrival of molecules per symbol duration in a SISO MCvD system using Binomial, Poisson, and Gaussian model approximations with MATLAB.}
            \resumeItem{Ran Monte Carlo simulations of the Gaussian model to encode/decode randomized binary sequences in a SISO MCvD system using BCSK modulation technique and calculated the bit error rate (BER) on Z-channel.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd
